\subsection{Related Work}
\label{comesh:section:related_work}


\noindent \textbf{IoT Application Management: }
IoT application management systems mostly use a central control plane, 
e.g.,  HomeOS \cite{HomeOS}.
Rivulet~\cite{rivulet} is distributed and uses \smart{}s to exchange messages and backup state to shadow nodes, focusing on fault-tolerance.
IoT fault-tolerance works also include WuKong~\cite{Wukong},
but similar to Rivulet, it does not manage routine execution. 
To the best of our knowledge, \sysname{} is the first decentralized IoT routine management system.
{Finally, while smart buildings are not delay-tolerant networks (DTNs)~\cite{fall2003delay}, \sysname's design addresses many concerns that also arise in DTNs, namely churn, failures, etc.}

\noindent \textbf{Consistent Hashing \& Committees: }
P2P systems such as Chord~\cite{chord}, Dynamo~\cite{dynamo},
employ consistent hashing.
to find the node storing a key-value pair.
\sysname{}'s \kgroup{} mechanism is inspired by consistent subgroups used by the election protocol in \cite{large_election}, but that mechanism is neither dynamic, nor intended for IoT settings, nor has locality. 

\noindent \textbf{Quorums and Agreement: }
Quorums have been used for coordinating
sensor networks' sleep schedules~\cite{heterogenous-quorum},
localization~\cite{scalable-quorums}, etc.
Agreement protocols for wireless topologies include 
Wireless Paxos~\cite{wirelesspaxos} and  WSN Byzantine consensus~\cite{wchain}.
These require many message exchange rounds, but
\sysname{}'s \kgroups{}
require only one round and ensure safety.
Blockchain- and edge-centric consensus schemes~\cite{khalid2020decentralized,yeow2017decentralized,xu2018blendcac}
have been proposed for access control, authentication, but not in the context of routine management.

\noindent \textbf{Load balancing: } 
Load balancing has long been studied in internet-based, p2p, and cloud distributed systems~\cite{mizan},
and for the edge~\cite{presto}.
In ad-hoc/mesh networks, load balancing has been explored for power-aware routing~\cite{1561947}. 
Load balancing has also targeted edge-cloud~\cite{nezami2021decentralized} {or edge-fog hybrids, like EdgeMesh~\cite{sahni2017edge}}.
Locality-aware consistent hashing has been used in serverless settings~\cite{hpdc2022locality},
unlike \sysname.
