\abstract{
The Internet of Things has instrumented billions of homes, buildings, farms, and factories
with smart devices, creating densely populated edge computing environments where automated
routines---chaining sensor readings to device actuations---determine how occupants live and
work. Yet today's platforms fail along two complementary dimensions. On the
\textit{system-facing} side, IoT control is routed through vendor clouds and central hubs
that introduce latency, cost, and single points of failure, even as the compute capacity
needed for local control already sits idle in the deployed devices themselves. On the
\textit{user-facing} side, occupants navigate a rich spectrum of control options---from
physical device interaction to proxy-based centralized hubs---with no structured system
support for moving between them, while the fire-and-forget RPC primitive gives developers
and users no feedback on whether physical actions have actually succeeded.

This dissertation advances a \textit{resilient, people-centric} vision for smart space
control through three orthogonal contributions, each targeting a distinct dimension of
the problem.

\textbf{CoMesh} addresses the \textit{infrastructure} dimension: where does
Sense-Trigger-Actuate logic execute? We present the first fully decentralized, hub-less
control plane for STA operations in large commercial edge IoT mesh networks. CoMesh
organizes devices into self-managing coteries using zero-message exchange protocols,
quorum-based agreement, epoch-based migration, and locality-sensitive hashing. We formally
prove its safety, liveness, and progress properties, and evaluate it on Raspberry Pi
deployments and large-scale simulations, demonstrating scalability, fault-tolerance, and
low latency without cloud or hub dependency.

\textbf{Control in Context} addresses the \textit{user-interaction} dimension: how do
occupants navigate smart space control? We present a mixed-methods study characterizing
how and why smart home users move along the spectrum from physical per-device interaction
to proxy-based centralized control. Through a survey of $N=60$ smart home owners and
semi-structured interviews with $N=8$ participants, we reveal that control is a fluid,
situational process shaped by reliability, convenience, and cognitive load---not by
ecosystem boundaries---and that today's platforms, designed around vendor interests
rather than user needs, leave occupants to build their own workarounds and absorb the
costs of inadequate infrastructure support.

\textbf{RASC} addresses the \textit{control-abstraction} dimension: what does the
underlying control primitive communicate? We introduce RASC (Request-Ack-Start-Complete),
a new abstraction that exposes the full lifecycle of every IoT device action, and Rascal,
its implementation atop existing RPC-based IoT platforms without requiring device
modifications. An adaptive polling strategy detects action start, completion, and failure
with minimal overhead; DAG-aware scheduling enables causally dependent automations that
react dynamically to action outcomes. Evaluation on real smart home workloads shows action
completion detection within 2--16 seconds over 90\% of cases and scheduling improvements
of 10--55\% over state-of-the-art baselines.

Together, these contributions turn the key dimensions of smart space control---where STA
logic runs, how users interact with it, and what the control primitive communicates---from
sources of fragility and frustration into first-class design targets, advancing the goal of
smart spaces that are autonomous, observable, and designed around the people who inhabit
them.
}
