\subsection{Interview Script}
\label{cic:appdx:interview}
Thank you so much for agreeing to participate in our interview. The purpose of this interview is to understand user experiences and perceptions with smart home device control, and how these perceptions change over time. Your responses will provide valuable information to help answer our research questions. Please keep in mind that this interview is not a test of your knowledge, but a way to learn from your experiences; there are no right or wrong answers. Some of these questions are meant to build upon your responses in the survey you previously completed. However, feel free to correct information provided in the survey or to add more context. 

I hope you had time to review a copy of the consent form for this study previously, before replying that you are willing to participate, but we want to be sure that you understand everything -- any questions about the consent form? 

Answer any questions regarding the consent form that they may have…

My collaborator [INSERT NAME] is here with me today and will be taking some notes during the interview.

As specified in the consent form, we will be audio recording and screen capturing this interview. After we get your permission, we will use Zoom to record the video and audio of this call. We will not be storing your name and personal information without explicitly telling you ahead of time. After today's interview, we will replace your personal information with a user code and keep your identity confidential. We will be referring to this user code when discussing and analyzing the data. You will not be identified in any publications. 

If at any point you can't hear me, or have connection issues, feel free to use the text chat feature to let me know. If you get disconnected from the video chat, please rejoin the meeting when your connection stabilizes (we'll wait for you). 

I will begin recording now, is that okay with you?

\subsubsection{Smart Home Setup}
Talk about the specific device that the participant mentioned in the survey:
In the survey, you mentioned that you control [INSERT DEVICE HERE] primarily through [INSERT CONTROL SCHEME HERE]. Have you ever tried controlling this device differently?
\begin{itemize}
    \item If yes: How did that experience go?
    \item If no: Do you feel that this way is sufficient for all your current goals with this device? 
        \begin{itemize}
            \item If not: Can you think of an experience where you felt like how you control this device has led to problems?
            \item If yes: Do you see a situation where your goals may change with this device, and this way of controlling it is no longer sufficient?
        \end{itemize}
\end{itemize}
Do you think that there is an ideal way to control your devices that may or may not exist currently?
\begin{itemize}
    \item If yes: can you describe it?
    \item If no: do you think that central control could be ideal? Why or why not?
        \begin{itemize}
            \item If yes: What device is your voice command set up with? What do you dislike most about your voice commands? How do you think about the relationship between your central manager and the device-specific app?
        \end{itemize}
\end{itemize}
Devices in a smart home can be set up in a way that they work together. For example, when the AC starts working, doors and windows are closed. Do those capabilities sound familiar?
Have you set up your smart home in a way that your devices work together?
\begin{itemize}
    \item If not: Do you feel like you are able to accomplish your goals without this? How could you benefit from a connected setup where devices could work in coordination with each other? How might that kind of setup concern you, if at all?
    \item If yes: How do you benefit from such a setup? Do you feel like this option is a gamechanger in any way?
    \item How might a setup that includes sensors benefit you?
    \item Did you set up your routines on your own?
    \item Is there any option to set it up on the device app itself?
    \item Why did you pick the central manager to set it up on?
\end{itemize}

Have you ever encountered devices that wouldn't effectively integrate into your existing smart home? By effectively, I mean that device collaborations are set up and proceed seamlessly.
\begin{itemize}
    \item If yes: What did you do?
    \item Do you ever consider how a device you might buy will work with other devices already in your home before purchasing it?
    \item Do you think about how you will control a device before you purchase it? Did you have specific goals in mind before you purchased a device?
    \begin{itemize}
        \item If yes: Have you ever experienced a situation where your expectation of controlling a device was different than reality?
        \begin{itemize}
            \item If yes: Has this caused you to change your expectations or goals with that specific device?
        \end{itemize} 
        \item If yes: Did your goals change after you purchased your device?
    \end{itemize}
\end{itemize}

\subsubsection{Smart Home Device Control}
Talk about the specific device that the participant mentioned in the survey:

\begin{itemize}
    \item In the survey, you mentioned that you control [INSERT DEVICE HERE] primarily through [INSERT CONTROL SCHEME HERE]. Have you ever tried controlling this device differently?
    \begin{itemize}
        \item \textit{If yes}: How did that experience go?
        \item \textit{If no}: Do you feel that this way is sufficient for all your current goals with this device? 
        \begin{itemize}
            \item \textit{If not}: Can you think of an experience where you felt like how you control this device has led to problems?
            \item \textit{If yes:} Do you see a situation where your goals may change with this device, and this way of controlling it is no longer sufficient?
        \end{itemize}
    \end{itemize}
\end{itemize}
\begin{itemize}
    \item Do you think that there is an ideal way to control your devices that may or may not exist currently?
    \begin{itemize}
        \item I\textit{f yes}: can you describe it?
        \item \textit{If no}: do you think that central control could be ideal? Why or why not?
        \begin{itemize}
            \item If yes: What device is your voice command set up with? What do you dislike most about your voice commands? How do you think about the relationship between your central manager and the device-specific app?
        \end{itemize}
    \end{itemize}
\end{itemize}
\begin{itemize}
    \item Devices in a smart home can be set up in a way that they work together. For example, when the AC starts working, doors and windows are closed. Do those capabilities sound familiar?
\end{itemize}
\begin{itemize}
    \item Have you set up your smart home in a way that your devices work together?
    \begin{itemize}
        \item \textit{If not}: Do you feel like you are able to accomplish your goals without this? How could you benefit from a connected setup where devices could work in coordination with each other? How might that kind of setup concern you, if at all?
        \item \textit{If yes}: How do you benefit from such a setup? Do you feel like this option is a gamechanger in any way?
        \item How might a setup that includes sensors benefit you?
        \item Did you set up your routines on your own?
        \item Is there any option to set it up on the device app itself?
        \item Why did you pick the central manager to set it up on?
    \end{itemize}
\end{itemize}
\begin{itemize}
    \item Have you ever encountered devices that wouldn't effectively integrate into your existing smart home? By effectively, I mean that device collaborations are set up and proceed seamlessly.
    \begin{itemize}
        \item \textit{If yes}: What did you do?
        \item Do you ever consider how a device you might buy will work with other devices already in your home before purchasing it?
        \item Do you think about how you will control a device before you purchase it? Did you have specific goals in mind before you purchased a device?
        \begin{itemize}
            \item \textit{If yes:} Have you ever experienced a situation where your expectation of controlling a device was different than reality?
                \begin{itemize}
                    \item \textit{If yes:} Has this caused you to change your expectations or goals with that specific device?
                \end{itemize}
            \item \textit{If yes}: Did your goals change after you purchased your device?
        \end{itemize}
    \end{itemize}
\end{itemize}
\begin{itemize}
    \item \textit{If they have more than 8 applications}: You mentioned that you have a lot of applications on your phone for controlling smart devices. How do you manage this? 
\end{itemize}


\subsubsection{Smart Home Errors and Exceptions}

\textit{If the participant stated that they're experiencing problems with their smart devices}
\begin{itemize}
    \item You mentioned that you experience issues with smart devices.
    \item How do you verify that an action actually takes place on a smart device?
    \item Can you tell me about the most memorable or recent failure of a smart device? How did it happen the first time? Do you see a pattern in the failures?
    \item Has your trust in any specific devices been affected after experiencing issues with them?
    \item Have any issues affected your willingness to purchase specific types of devices?
    \begin{itemize}
        \item \textit{If yes}: Which ones? What was the issue you experienced with these devices?
    \end{itemize}
\end{itemize}
\textit{If the participant mentioned that they have encountered problems with (a) specific pair(s) of devices from different vendors:}
\begin{itemize}
    \item In the survey, you told us that some vendors' devices do not work well with each other. Specifically, you experienced problems while trying to integrate/integrating [INSERT DEVICE A] with [INSERT DEVICE B]. Can you share more instances of the same problem with different pairs of devices? What were you trying to accomplish with each pairing?
\end{itemize}
\textit{If not}:
\begin{itemize}
    \item Have you encountered any issues in making devices from different vendors work together? What were those issues?
    \begin{itemize}
        \item \textit{If yes}: What were those issues?
    \end{itemize}
\end{itemize}
\textit{If the participant mentioned that they have stopped using or returned a specific device because it wasn't working for them}: 
\begin{itemize}
    \item You mentioned that you stopped using or returned [insert specific device] because it wasn't working properly. Did you replace that device in your home with something else? 
    \begin{itemize}
        \item \textit{If yes}, what did you consider when choosing a replacement device?
        \item \textit{If not}, did you decide to not try and accomplish what you wanted to with [insert specific device]?
    \end{itemize}
\end{itemize}

\subsubsection{Smart Home Troubleshooting}
\begin{itemize}
    \item In the survey, you talked about your troubleshooting process as this set of steps [Insert answer from the survey]
    \begin{itemize}
        \item \textit{Go through the steps, and if any of them seem particularly interesting or not detailed enough, ask}: Could you explain a little more about what you mean when you say you [DO X]?
        \item Do you find that there is an approach that universally helps you fix problems that come up in your smart home?
        \item What was the most difficult and memorable process you went through to get a device or automation to work in your smart home?
    \end{itemize}
\end{itemize}
\textit{If the participant mentions that they have given up on a device before}:
\begin{itemize}
    \item You mentioned that you gave up on getting [insert device name] to work in your home. Have you decided to get other devices to work on your home? 
    \begin{itemize}
        \item Was the process of getting to this point similar to what you described for [insert device name]?
    \end{itemize}
\end{itemize}


