\subsection{Limitations and Future Work}
\label{cic:sec:limitations}
Our methodology used surveys and interviews to elicit responses from participants regarding their past experiences and current perceptions. 

Future research should look to expand on this work through studies that focus on clear categories of smart home owners, based on characteristics such as location (e.g., temperate zones vs. frigid vs. coastal), size of home (apartment vs. single-family home vs. mansion), and other factors. In addition, our survey respondents and interview participants likely skewed more towards a tech-savvy population, especially given that we recruited using Prolific~\cite{abrokwa2021comparing}. Thus, future work can also explore perceptions and experiences of users who may be overall less aware of smart home device capabilities. %Such work could build on our results and also reveal new findings. 
% 
In addition, surveys and interviews rely on participants to reflect on their interactions with smart home devices, rather than having the research team observe these interactions directly. Future work can utilize more observational methodologies and ethnographic studies to expand our results by providing additional context on how participants control their devices. 

%\igc{not sure if this is limitations. this seems to be repetition of what was already in the discussion... recommend removing entire para}
%Future work should also develop prototypes of systems outlined in \Cref{cic:sec:discussion} and test them with real smart home device users. Such work would build upon the design principles laid out in this paper. By leveraging the empirical results of this paper, future work can look to more artifact-based contributions while still using our results to ensure that their systems are ``user-centric,'' because their design is grounded in existing user perceptions and desires~\cite{kim2020developing}. 

%\igc{The reviewer who reads the paper will notice that earlier in the paper we make some statements (and claims?) about addressing guests and multiple users, and yet we have this para that says we don't do anything about multiple users. }

Our results are tied to the technology mix used during data collection. However, as technology evolves and matures, and new standards such as Matter~\cite{matter} emerge, future work can incorporate our broader implications and findings into its design. Interaction patterns related to user transitions across the control spectrum will remain even as such standards develop, which will require future research to use our approach to understand \textit{how} users' interaction patterns change with these standards in place.

%Even as multibrand hubs gain traction and standards such as Matter~\cite{matter} become more popular, association and recovery flows are expected to improve, potentially reducing some of the frictions we document. \igc{I'm not sure I agree with that last sentence. Matter will help to standardize across vendors, yes. But in terms of improving flows, that is up in the air. I would remove that sentence or make its claim milder. Standards in systems fields have a very hard time to catch on! (e.g., what is a ``standard OS'' that people use? The answer is not one, but it is Linux, FreeBSD, MacOS, Windows,...} However, our work provides a snapshot of the current state of smart home control, and our findings can guide future work aimed at addressing these existing issues.} \igc{I actually don't understand what this entire para is trying to say. Perhaps instead just say sth like, ``As technology evolves and matures and as new standards like Matter [] emerge, this presents a great opportunity for the community to incorporate several of our findings and recommendations.'' }

Our work focused primarily on a single user in a smart home; while participants did discuss how other users in the home influenced their perceptions and preferences, our study elicited only one opinion from each smart home. Previous work has described smart homes as more sociotechnical systems, often containing multiple users with diverse experiences, desires, and perceptions~\cite{geeng2019s}. Future work should more explicitly consider the sociotechnical nature by conducting studies with multiple users in the same home, examining how control schemes and methods in a single household affect different users in a smart home, and building upon the perspectives elicited in this work. 

